---
title: "The AU's library of R functions"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "")

library(tidyverse)
library(ggplot2)
library(aulib)
```


R package for MLITSD's Analytics Units.

## Installation   

Install the most updated version using `remotes::install_github()`  
```
remotes::install_github("ETDAU/aulib")
```

Or, a source package using `devtools::install_github()`    
```
devtools::install_github("https://github.com/ETDAU/aulib/releases/tag/v0.0.0.9000")
```


## Functions   

### `au_palette()`      
`au_palette()` provides a palette of accessible colours that are recommended by the [OPS](https://intra.ontario.ca/tbs/ontario-logo) (`palette = "ops"`) and are commonly used in the analytics units (`palette = "au"`).  


```{r}
# create fake data 
tibble(w = sample(LETTERS[1:6], size = 100, replace = T)) %>%
  count(w) %>% 
  # create a bar graph with the fake data  
  ggplot(aes(x = w,
             y = n,
             fill = w)) +
  geom_bar(stat = "identity",
           position = position_dodge(.8)) + 
  scale_fill_manual(guide = "none",
                    # using AU palette (Or leave the argument blank; `au_palette()`)
                    values = au_palette(palette = "au")) +
  scale_y_continuous("Count") +
  scale_x_discrete("") + 
  theme_classic()
```

You can use both `ops` and `au` palettes by leaving the argument empty: `au_palette()`.    


### `make_ca_connection()`       
`make_ca_connection()` creates a connection object using an ODBC driver with the log-in credentials saved as the system environment variables as "userid" (user ID) and "pwd" (password). For saving your credentials in your `.Renviron`, check this [instruction](https://github.com/ETDAU/aulib/blob/main/vignettes/odbc-credentials.Rmd).      

```
con = make_ca_connection()
```

### `rm_dup_response()`   
`rm_dup_response()` is a helper function for cleaning duplicated responses that are concatenated (e.g., "yes, yes"). 

```{r}
# create a vector of strings with some duplicated responses
tibble(duplicated_response = c("yes, yes", "no", "yes, no", "YES, yes")) %>% 
  # apply `rm_dup_responses()` to clean the duplicated_response column  
  mutate(clean_response = rm_dup_responses(duplicated_response, 
                                           sep = ","))
```


### `binary_to_numeric()`    
`binary_to_numeric()` converts "yes" and "no" responses to numeric values of 1 and 0, respectively.  


```{r}
# create a string of binary responses
tibble(binary_response = c(sample(c("yes", "no"), 6, replace = TRUE), "YES")) %>% 
  # apply `binary_to_numeric()` to convert into numeric values 
  mutate(numeric_response = binary_to_numeric(binary_response))
```


### `clean_query()`    
`clean_query()` is a function created by [Tori Oblad](https://stackoverflow.com/a/58446028) that facilitates importing `.sql` queries into R by removing comment lines and line breaks from queries. 



