---
title: "Use ODBC login as environment variables"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use ODBC login as environment variables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(aulib)
```

# Save ODBC log-in credentials    

You can use `.Renviron` file to store log-in credentials of the ODBC database, which can be retrieved by running `Sys.getenv()`.   

1. Edit or create an `.Renviron` file in your home directory either:   
  + manually     
  + or, using `usethis` package:    

```{r eval = FALSE}
# (Optional) install `usethis` package, if you do not have the package installed already
install.packages("usethis") 

# create a .Renviron file
usethis::edit_r_environ()
```

2. Save the credentials in the `.Renviron` file:    
```
userid = "my_username"
pwd = "my_password"
```
You can change the name of the parameters (e.g., "odbc_id" instead of "user_id"), but make sure to use your chosen parameter names to retrieve these credentials saved as environment variables.   

3. Retrieve the credentials using `Sys.getenv()`:    
```{r eval = FALSE}
Sys.getenv("userid") # user ID; change the name of the quoted parameter based on the name chosen
Sys.getenv("pwd") # password 
```

These environment variables can be plugged into functions. For example, while openning a connection:     
```{r eval = FALSE}
con = odbc::dbConnect(odbc::odbc(),
                      uid = Sys.getenv("userid"),
                      pwd = Sys.getenv("pwd"))
```


